---
title: "Untitled"
author: "Rabya Ghafoor"
date: "4/1/2020"
output: pdf_document
---
```{r}
library(dplyr)
library(gutenbergr)
library(stringr)
library(scales)
library(tidytext)
library(janeaustenr)
library(tidyr)
library(ggplot2)
```

Exercise #1
```{r}
orig_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text,
                                     regex("^chapter [\\divxlc]",
                                           ignore_case = TRUE)))) %>%
  ungroup() %>%
  select(chapter, linenumber, everything())
orig_books
```

```{r}
tidy_books <- orig_books %>%
  unnest_tokens(word, text) %>%
# use str_extract because some gutenberg texts have other symbols around
# the words as part of the encoding
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)
```
```{r}
tidy_books %>%
  count(word, sort = TRUE)
```




```{r}
hgwells <-  gutenberg_works(author == "Wells, H. G. (Herbert George)") 
bronte <- gutenberg_works(author ==  "Brontë, Charlotte" | author ==  "Brontë, Anne" | author == "Brontë, Emily" ) 
```

```{r}
hgwells <- hgwells %>% gutenberg_download()
```
```{r}
bronte <- bronte %>% gutenberg_download()
```
```{r}
tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)
tidy_hgwells %>%
  count(word, sort = TRUE)
tidy_bronte %>%
  count(word, sort = TRUE)

```

```{r}
frequency_by_word_across_authors <- bind_rows(mutate(tidy_bronte,
author = "Bronte"),
mutate(tidy_hgwells, author = "Wells"),
mutate(tidy_books, author = "Austen")) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(author, proportion)
frequency_by_word_across_authors
```

```{r}
frequency <- frequency_by_word_across_authors %>%
  gather(author, proportion, `Bronte`:`Wells`)
frequency
```

```{r}
#Compare word frequency by author to Austen
frequency %>% ggplot(aes(x = proportion,
                         y = `Austen`,
                         color = abs(`Austen` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5,
              width = 0.3, height = 0.3) +
  geom_text(aes(label = word),
            check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001),
                       low = "darkslategray4",
                       high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Jane Austen", x = NULL)
```
We can tell that Austen and Bronte are more similar (grouped closer to the line) than Austen and Wells.
Let’s use a correlation test to quantify the amounts.


```{r}
df_Bronte <- frequency[frequency$author == "Bronte",]
df_Bronte
```
```{r}
cor.test(data = df_Bronte, ~ proportion + `Austen`)
```

```{r}
df_Wells <- frequency[frequency$author == "Wells",]
df_Wells
```

```{r}
cor.test(data = df_Wells, ~ proportion + `Austen`)
```

Exercise #2

```{r}
jearle <-  gutenberg_works(author == "Earle, John") 
meale <- gutenberg_works(author == "Eales, Mary") 
dok <- gutenberg_works(author == "Oakey, Daniel") 
```


```{r}
jearle <- jearle %>% gutenberg_download()
```
```{r}
meale <- meale %>% gutenberg_download()
```

```{r}
dok <- dok %>% gutenberg_download()
```

```{r}
#tidy data, remove stopwards

tidy_jearle <- jearle %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)

tidy_meale <- meale %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)

tidy_dok <- dok %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)

tidy_jearle %>%
  count(word, sort = TRUE)
tidy_meale %>%
  count(word, sort = TRUE)
tidy_dok %>%
  count(word, sort = TRUE)
```


```{r}

frequency_by_word_across_authors_new <- bind_rows(mutate(tidy_jearle,
author = "Earle"),
mutate(tidy_meale, author = "Eales"),
mutate(tidy_dok, author = "Oakey")) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(author, proportion)
frequency_by_word_across_authors_new
```
```{r}
frequency1 <- frequency_by_word_across_authors_new %>%
  gather(author, proportion, `Earle`:`Oakey`)
frequency1
```



```{r}
frequency1 %>% ggplot(aes(x = proportion,
                         y = `Eales`,
                         color = abs(`Eales` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5,
              width = 0.3, height = 0.3) +
  geom_text(aes(label = word),
            check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001),
                       low = "darkslategray4",
                       high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Mary Eales", x = NULL)
```

```{r}
df_Earle <- frequency1[frequency1$author == "Earle",]
df_Earle
```

```{r}
df_Oakey <- frequency1[frequency1$author == "Oakey",]
df_Oakey
```

```{r}
cor.test(data = df_Earle, ~ proportion + `Eales`)
```
```{r}
cor.test(data = df_Oakey, ~ proportion + `Eales`)
```

According to the graph we can tell that Eales and Earle are more similar (words are grouped closer to the line) than Eales and Okaey. The correlation test is consistent with these findings as the correlation coeffecient between Eales and Earle is slightly larger (0.16) than Eales and Oakey (0.11).

Exercise #3
```{r}
library(textdata)
```
```{r}
sentiments
sentiments %>% arrange(word)
```

```{r}
cdic <- gutenberg_works(author == "Dickens, Charles") %>% filter(title == "A Tale of Two Cities")
cdic <- cdic %>% gutenberg_download()
```

```{r}
tidy_cdic <- cdic %>%
  unnest_tokens(word, text) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  anti_join(stop_words)
tidy_cdic %>%
  count(word, sort = TRUE)
```
```{r}
# select only the words from the nrc lexicon that are "fear" words
install.packages("bing")
```
```{r}

